Time--Frequency Scattering Accurately Models Auditory Similarities Between Instrumental Playing Techniques

### 2020-07-19 paper/paper.tex
update Figure 6 and its caption
bis

\begin{figure}[h!]
\includegraphics[width=0.9\textwidth]{figures/ablationStudy}
\caption{\csentence{Impact of different processing architecture or protocol designs.} For each condition, the central mark indicates the median, and the bottom and top edges of the box indicate the 25th and 75th percentiles, respectively. The whiskers extend to the most extreme data points not considered outliers. Performance achieved for each reference clustering is depicted by a losange whose color is chosen arbitrarily but consistently across conditions.
See \lnameref{sec:discussion} section for details.}
\label{fig:ablation}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=0.9\textwidth]{figures/ablationStudy}
\caption{\csentence{Impact of different processing architecture or protocol designs.} For each condition, the central mark indicates the median, and the bottom and top edges of the box indicate the 25th and 75th percentiles, respectively. The performance achieved for each reference clustering is depicted by a lozenge whose color is chosen arbitrarily but consistently across conditions.
See \lnameref{sec:discussion} section for details.}
\label{fig:ablation}
\end{figure}
